Lifespan analysis

### 2023-06-07 stats/lifespan.Rmd
save lifespan models from server

```{r plot}
lifespan <- lifespan_data %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan, "../saves/lifespan.rds")
```

@@

write.csv(mlinear, "../saves/mlinear.csv", quote = F, row.names = F)
saveRDS(mlinear, "../saves/mlinear.rds")

@@

write.csv(mquadratic, "../saves/mquadratic.csv", quote = F, row.names = F)
saveRDS(mquadratic, "../saves/mquadratic.rds")

@@

write.csv(mcubic, "../saves/mcubic.csv", quote = F, row.names = F)
saveRDS(mcubic, "../saves/mcubic.rds")

@@

write.csv(mgaussianprocess, "../saves/mgaussianprocess.csv", quote = F, row.names = F)
saveRDS(mgaussianprocess, "../saves/mgaussianprocess.rds")

@@

conditional_smooths(msplines2, effects = "weight")

write.csv(msplines, "../saves/msplines.csv", quote = F, row.names = F)
saveRDS(msplines, "../saves/msplines.rds")

@@

write.csv(msplines2, "../saves/msplines2.csv", quote = F, row.names = F)
saveRDS(msplines2, "../saves/msplines2.rds")

@@

write.csv(msplines3, "../saves/msplines3.csv", quote = F, row.names = F)
saveRDS(msplines3, "../saves/msplines3.rds")

@@

write.csv(msplines4, "../saves/msplines4.csv", quote = F, row.names = F)
saveRDS(msplines4, "../saves/msplines4.rds")

@@

write.csv(msplines5, "../saves/msplines5.csv", quote = F, row.names = F)
saveRDS(msplines5, "../saves/msplines5.rds")
```

```{r lifespan_modelcomparison}
# mlinear <- readRDS("../saves/mlinear.rds")
# mquadratic <- readRDS("../saves/mquadratic.rds")
# mcubic <- readRDS("../saves/mcubic.rds")
# mgaussianprocess <- readRDS("../saves/mgaussianprocess.rds")
# msplines <- readRDS("../saves/msplines.rds")

@@

write.csv(mcomparison, "../saves/mcomparison.csv", quote = F, row.names = F)
saveRDS(mcomparison, "../saves/mcomparison.rds")
```

```{r prediction_plot_winning_model}
prediction_plot <- mdata %>%
  add_predicted_draws(msplines) %>%  # adding the posterior distribution
  ggplot(aes(x = age_centered, y = mean_dist)) +  
  geom_jitter(data = mdata, colour = "grey", size = 1.5, alpha = 0.8) + 
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .80), alpha = 0.5, colour = "black") +
  scale_fill_brewer(palette = "Greys") + 
  scale_y_continuous(limits = c(0,4))

>>>>

```{r plot}
lifespan_plot <- lifespan_data %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

# ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
```

@@

write.csv(mlinear, "../saves/lifespan_mlinear.csv", quote = F, row.names = F)
saveRDS(mlinear, "../saves/lifespan_mlinear.rds")

@@

write.csv(mquadratic, "../saves/lifespan_mquadratic.csv", quote = F, row.names = F)
saveRDS(mquadratic, "../saves/lifespan_mquadratic.rds")

@@

write.csv(mcubic, "../saves/lifespan_mcubic.csv", quote = F, row.names = F)
saveRDS(mcubic, "../saves/lifespan_mcubic.rds")

@@

write.csv(mgaussianprocess, "../saves/lifespan_mgaussianprocess.csv", quote = F, row.names = F)
saveRDS(mgaussianprocess, "../saves/lifespan_mgaussianprocess.rds")

@@

write.csv(msplines, "../saves/lifespan_msplines.csv", quote = F, row.names = F)
saveRDS(msplines, "../saves/lifespan_msplines.rds")

@@

write.csv(msplines2, "../saves/lifespan_msplines2.csv", quote = F, row.names = F)
saveRDS(msplines2, "../saves/lifespan_msplines2.rds")

@@

write.csv(msplines3, "../saves/lifespan_msplines3.csv", quote = F, row.names = F)
saveRDS(msplines3, "../saves/lifespan_msplines3.rds")

@@

write.csv(msplines4, "../saves/lifespan_msplines4.csv", quote = F, row.names = F)
saveRDS(msplines4, "../saves/lifespan_msplines4.rds")

@@

write.csv(msplines5, "../saves/lifespan_msplines5.csv", quote = F, row.names = F)
saveRDS(msplines5, "../saves/lifespan_msplines5.rds")
```

```{r lifespan_modelcomparison}
# mlinear <- readRDS("../saves/lifespan_mlinear.rds")
# mquadratic <- readRDS("../saves/lifespan_mquadratic.rds")
# mcubic <- readRDS("../saves/lifespan_mcubic.rds")
# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
# msplines <- readRDS("../saves/lifespan_msplines.rds")

@@

write.csv(mcomparison, "../saves/lifespan_mcomparison.csv", quote = F, row.names = F)
saveRDS(mcomparison, "../saves/lifespan_mcomparison.rds")
```

```{r prediction_plot_winning_model}
 mdraws <- mdata %>%
  add_predicted_draws(msplines) %>% 
  ungroup() %>% 
  select(-c(.row, .chain, .iteration)) %>%
  rename(draw = .draw, predicted_value = .prediction)

write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
saveRDS(mdraws, "../saves/lifespan_mdraws.rds")

prediction_plot <- mdraws %>%
  ggplot(aes(x = age)) +  
  geom_jitter(aes(y = mean_dist), colour = "grey", size = 1.5, alpha = 0.8) + 
  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66") +
  scale_fill_brewer(palette = "Greys") + 
  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0,4)) + 
  guides(fill = "none") +
  labs(x = "Age in years", y = "Mean click distance in target widths", fill = "")
